ODGI: scalable tools for pangenome graphs

### 2021-06-02 manuscript/main.tex
reduced the noise

    \corresp{$^\ast$To whom correspondence should be addressed.}

@@

    \indent \topic{odgi build, view \& validate} pangenome graphs can be
    stored in the textual Graphical Fragment Assembly
    (GFAv1) format\citep{GFA}; \cmd{odgi build} and \cmd{odgi view}
    convert graphs from GFA to the \odgi\ format and \textit{vice versa}.
    \cmd{odgi validate} ascertains the graph data is correct, e.g.,
    it validates paths with respect the graph topology.

    \topic{odgi viz, sort, draw \& layout} pangenome visualisation
    provides convenient insight into genomic variation. \cmd{odgi viz}
    generates a linearized representation of the pangenome and is
    capable of handling full length human chromosomes
    (see Fig.~\ref{fig:1}a). \cmd{odgi sort} reorganises node order and
    simplifies the graph by applying several algorithms, including the
    novel `path-guided stochastic gradient descent' algorithm.
    \cmd{odgi layout} generates a file with the X-Y coordinates for
    all nodes and \cmd{odgi draw} draws a layout of the graph
    (Fig.~\ref{fig:1}b).

    \topic{odgi stats, bin, depth \& degree} pangenome numerical
    counts provide insight into genome complexity in other
    ways. E.g., \cmd{odgi stats} returns the number of nodes,
    edges, paths, and graph length. \cmd{odgi bin} summarises path
    information into bins of a specified size, thereby enabling a
    summarised view of large genomes. \cmd{odgi depth} and
    \cmd{odgi degree} return the node depth and degree as defined by
    user provided criteria. These methods allow detection of complex
    genomic regions.

@@

    \topic{odgi explode, squeeze \& extract} pangenome are constructed
    as a large graph. \cmd{odgi explode} separates units, such as
    chromosomes, into different files.  \cmd{odgi squeeze} merges
    multiple graphs into the same file whilst preventing node ID
    collisions. \cmd{odgi extract} extracts regions of the graph as
    defined by certain criteria, allowing downstream processing of
    smaller subgraphs.

>>>>

    \corresp{$^\dagger$To whom correspondence should be addressed.}

@@

    \indent \topic{odgi build, view \& validate} pangenome graphs can be
    stored in the textual Graphical Fragment Assembly
    (GFAv1) format\citep{GFA}. \cmd{odgi build} and \cmd{odgi view}
    convert graphs from GFA to the \odgi\ format and \textit{vice versa}.
    \cmd{odgi validate} ascertains the graph data is correct, e.g.,
    it validates paths with respect the graph topology.

    \topic{odgi viz, sort, draw \& layout} pangenome visualisation
    provides convenient insight into genomic variation. \cmd{odgi viz}
    generates a linearized representation of the pangenome and is
    capable of handling full length human chromosomes
    (see Fig.~\ref{fig:1}a). \cmd{odgi sort} reorganises node order and
    simplifies the graph by applying several algorithms, including the
    novel `path-guided stochastic gradient descent' algorithm.
    \cmd{odgi layout} generates a layout file with the X-Y coordinates for
    all nodes and \cmd{odgi draw} draws it, bringing the pangenome representation
    in two dimensions.

    \topic{odgi stats, bin, depth \& degree} pangenome numerical
    counts provide insight into genome complexity in other
    ways. \cmd{odgi stats} returns the number of nodes,
    edges, paths, and graph length. \cmd{odgi bin} summarises path
    information into bins of a specified size, thereby enabling a
    summarised view of large genomes. \cmd{odgi depth} and
    \cmd{odgi degree} return the node depth and degree as defined by
    user provided criteria. These methods allow detection of complex
    genomic regions.

@@

    \topic{odgi explode, squeeze \& extract} pangenomes are constructed
    as large graphs. \cmd{odgi explode} separates units, such as
    chromosomes, into different files.  \cmd{odgi squeeze} merges
    multiple graphs into the same file whilst preventing node ID
    collisions. \cmd{odgi extract} extracts regions of the graph as
    defined by certain criteria, allowing downstream processing of
    smaller subgraphs.
